Hippocampal replay of experience at real world speeds

### 2021-05-13 Article.tex
Update on Overleaf.

The brain has the remarkable ability to store and retrieve representations of past events, allowing memories of the past to influence the future. These memory processes depend critically on the hippocampus, where rapid plasticity during an experience is thought to drive the initial encoding of events \citep{EichenbaumCanWeReconcile2014}. Subsequently, hippocampal "replay" of stored representations during both slow-wave sleep and periods of immobility during waking contributes to the longer term storage and updating of event memories in distributed hippocampal-neocortical circuits \citep{Joohippocampalsharpwave2018}(REFs). Experiences can take place over many seconds, minutes, hours or days, and to be useful in guiding behavior, memories of these events must be stored in such a way that they can be retrieved quickly to inform upcoming choices. Consistent with this need for rapid storage, hippocampal replay events can express time compressed representations of past experience, activating regions outside the hippocampus and presumably driving plasticity in those regions to promote memory storage. \citep{CarrHippocampalreplayawake2011}.

@@

@@

\subsection*{Most replays contain coherent spatial content}

After testing our model on a single SWR event, we applied our clusterless decoding algorithm to hippocampal recordings from 10 rats performing the W-track spatial alternation task (\# tetrodes range: [10, 24], brain areas = [CA1, CA2, CA3]; some data previously used in \cite{KarlssonAwakereplayremote2009, KayConstantSubsecondCycling2020, CarrTransientSlowGamma2012}, position linearized to 1D). We first confirmed that our cell population for each animal could closely track the position of the animal during behavior by comparing the most probable decoded position to the position of the animal (with the caveat that theta sequences and replay sequences will represent positions other than where the animal is and our resolution is limited by the size of our 3 cm position bins). We found, similar to other studies, that the average median difference between actual and decoded location is small (4 cm median difference, 3-6 cm 95\% CI, for all time in sessions, 5 fold cross validation). Importantly, we achieved this using small time bins (2 ms) compared to the commonly used 250 ms time bin that most studies use for decoding during run, demonstrating the power of our algorithm. We also verified that the population spiking for all positions on the track was consistent for each animal (\FIGSUPP[2]{fig2sup3}).

>>>>

The brain has the remarkable ability to store and retrieve representations of past events, allowing memories of the past to influence the future. These memory processes depend critically on the hippocampus, where rapid plasticity during an experience is thought to drive the initial encoding of events \citep{EichenbaumCanWeReconcile2014}. Subsequently, hippocampal "replay" of stored representations during both slow-wave sleep and periods of immobility during waking contributes to the longer term storage and updating of event memories in distributed hippocampal-neocortical circuits \citep{Franklandorganizationrecentremote2005, Joohippocampalsharpwave2018}. Experiences can take place over many seconds, minutes, hours or days, and to be useful in guiding behavior, memories of these events must be stored in such a way that they can be retrieved quickly to inform upcoming choices. Consistent with this need for rapid storage, hippocampal replay events can express time compressed representations of past experience, activating regions outside the hippocampus and presumably driving plasticity in those regions to promote memory storage \citep{CarrHippocampalreplayawake2011}.

@@

\subsection*{Most replays contain coherent spatial content}
After testing our model on a single SWR event, we applied our clusterless decoding algorithm to hippocampal recordings from 10 rats performing the W-track spatial alternation task (\# tetrodes range: [10, 24], brain areas = [CA1, CA2, CA3]; some data previously used in \cite{KarlssonAwakereplayremote2009, KayConstantSubsecondCycling2020, CarrTransientSlowGamma2012}, position linearized to 1D). We first confirmed that our cell population for each animal could closely track the position of the animal during behavior by comparing the most probable decoded position to the position of the animal (with the caveat that theta sequences and replay sequences will represent positions other than where the animal is and our resolution is limited by the size of our 3 cm position bins). We found, similar to other studies, that the average median difference between actual and decoded location is small (4 cm median difference, 3-6 cm 95\% CI, for all time in sessions, 5 fold cross validation). Importantly, we achieved this using small time bins (2 ms) compared to the commonly used 250 ms time bin that most studies use for decoding during run, demonstrating the power of our algorithm. We also verified that the population spiking for all positions on the track was consistent for each animal (\FIGSUPP[2]{fig2sup3}).

@@
